A tool for designing digital filters for the Hankel and Fourier transforms in potential, diffusive, and wavefield modeling

### 2018-11-21 ManuscriptGeophysics2018.tex
Final figures

\subsection{Design}
Figures~\ref{fig:Figure-2} and~\ref{fig:Figure-3} show the solution spaces of
seven consecutive inversion runs using the following theoretical transform
pairs \citep[e.g.,][]{USGS.75.Anderson},
%
\begin{align}
  \int^\infty_0\,l \exp\left(-al^2\right) J_0(rl)\,dl &=
  \frac{1}{2a} \exp\left(\frac{-r^2}{4a}\right)\ , \\
  \int^\infty_0\,l^2 \exp\left(-al^2\right) J_1(rl)\,dl &=
  \frac{r}{4a^2} \exp\left(-\frac{r^2}{4a}\right)\ ,
  \label{eq:j01}
\end{align}
%
where $a$ was set to 5. In the algorithm you can provide one pair
for the inversion, and a different pair to get the minimum amplitude or the
maximum $r$. In this case the same transform pair was used for both the
inversion and the check of quality. The acceptable relative error was set to
1\,\%. The RHS evaluation parameter for the inversion was set so  that an
over-determined system was evaluated with $M = 2N$ equations, where $r_\mr{I}$
was logarithmically spaced from $\log_{10}[1/\max(b)] - 1$ to
$\log_{10}[1/\min(b)] + 1$, where $b$ are the filter abscissae as given in
equation~\ref{eq:base}. This is accomplished in \texttt{fdesign} by setting
parameter $r_\mr{def} = (1, 1, 2)$.

Figure~\ref{fig:Figure-2} shows three different inversion runs for $N=101$,
201, and 401 for a wide range of spacing and shift values.
From this one has to decide for a filter length. Longer filters tend to give
more precise results, but their transform is computationally more expensive as
more values have to be evaluated. The length of the filter does not has to be
an odd number, but many published filters do have an odd number of
coefficients. The integral runs from $-\infty$ to $+\infty$ and hence an odd
point filter comes naturally by truncating the integral to a finite sum from
$-(N-1)/2$ to $(N-1)/2$. However, this is only true if the shift value
$\delta = 0$. If it differs from zero then there is no advantage in having an
odd point filter.
%
\plot*{Figure-2}{width=\textwidth}{%
  Test of different filter lengths. Filter length is a trade-off between
    precision and speed, as shorter filters are faster but less precise, and
  longer filters are more precise but computationally more expensive. The red
  square in subplot (b) is the starting point of Figure~\ref{fig:Figure-3}.}%
%

Figure~\ref{fig:Figure-3} shows four consecutive inversion runs for $N=201$,
where each run is a focus on a subsection of the previous run, indicated by the
red square. From the low resolution overview runs (a) and (b) it looks like
this is a standard, straight-forward minimization problem. However, from the
more detailed results in (c) and (d) it becomes obvious that it is a
minimization problem that has to be solved stochastically, as there are
solutions with 2 orders of magnitude difference apparently randomly next to
each other.
%
\plot*{Figure-3}{width=\textwidth}{%
  Solution spaces of four consecutive inversion runs for a 201\,pt filter. Each
  consecutive run zooms into a portion of the previous solution space,
  indicated by the red square. The more in detail we obtain the solution space,
  the more random appears to be the distribution.}%
%

Figure~\ref{fig:Figure-4} shows in (a) the filter values for $J_0$ and $J_1$ of
the best 201 \old{point}\new{pt} filter obtained this way, and in (b) its
right-hand-side solution. The black dots indicate negative values, from which
it can \new{be} seen that adjacent values are often alternating between
positive and negative contributions.
%
\plot*{Figure-4}{width=.9\textwidth}{(a) Filter values of the best obtained
  201\,pt filter with the corresponding check of quality in (b). Black points
  indicate negative values, which shows that adjacent values have often
  opposite signs.}
%

Designing filters is to a large extent trial and error. All input variables
influence the outcome, and often an even better filter is found by sheer luck
of choosing the right starting parameters, as can be seen in
Figure~\ref{fig:Figure-4} (h). However, once you are in this zone every filter
is a very good filter. Each of the input parameters has an effect on the
outcome. It also depends heavily on the transform pairs $f_\mr{I;C}$; functions
that decay rapidly are generally better, as noted by earlier authors
\citep[e.g.][]{USGS.75.Anderson}. It also depends on the filter length, and
obviously heavily on the spacing and shift values. Another important point is
how you define the right-hand evaluation points of the inversion
($r_\mr{def}$). Evaluating corresponding transform pairs separately or jointly
also leads to different filter coefficients ($J_0$, $J_1$, or $J_0$ \& $J_1$,
or equally sine, cosine, or sine \& cosine); also if the real or the imaginary
part is used when complex transform pairs or \texttt{empymod} is used; and if
it is inverted for the minimum amplitude or for the maximum $r$.

@@

It is very important to note again that other scenarios might yield very
different error plots. Although the new 201\,pt filter proves to be very
accurate for these three models, it might not be the best filter in other
cases. To verify the applicability of the filter we run two different tests
over a wide range of scenarios. Figure~\ref{fig:error} shows the relative
errors of DLF using the filter \emph{Wer201} compared to QWE for a deep water
model \new{(2\,km water depth)}, a shallow water model \new{(400\,m water
depth)}, and a land model. The models consist of air (upper halfspace), a water
layer in the first two examples, and a subsurface halfspace. Source depth is
1990\,m, 10\,m, and 0.5\,m in the deep, shallow, and land case, respectively.
Receiver depth is 2000\,m, 100\,m, and 0.8\,m. The subsurface halfspace
resistivity varies from 1 to 10, 100, and 1000\,$\Omega\,$m from the left to
the right column. The error plots cover offsets from 50\,m to 20\,km on the
x-axis, and 0.01\,Hz to 10\,Hz on the y-axis. It can be seen in the result that
the filter is sufficiently precise for all practical CSEM cases, hence has
generally an error far below 1\,\% ($10^{-2}$) in all cases. A relative noise
of less than 1\,\% is generally considered really good for real data. The
exceptions are in the shallow water case at large offsets with relatively high
frequencies, e.g., 10\,km offset with 8\,Hz; this zone has a very high error
for subsurface resistivities of 1\,$\Omega\,$m and 10\,$\Omega\,$m (yellow
zones). However, this is due to the fact that the amplitudes of the signal for
these offsets and frequencies are in the order of $10^{-25}\,$V/m. The grey
contour lines in the plot indicate the power of the amplitude of the signal.
%
\plot*{error}{width=\textwidth}{Relative error plots comparing the DLF
  (\emph{Wer201}) with QWE for the three cases deep water (top row), shallow
  water (middle row), and land (bottom row). The subsurface halfspace
  resistivity varies from 1 to 1000\,$\Omega\,$m from the left column to the
  right column; offsets vary from 50\,m to 20\,km, and frequencies vary from
  0.01\,Hz to 10\,Hz. The DLF provides sufficiently accurate results for all
  practical CSEM applications. The exception is in the shallow water case for
  $\rho = 1\,\Omega\,$m and $10\,\Omega\,$m for large offsets and high
  frequencies (yellow zones). However, the amplitudes in these regions are in
  the order of $10^{-25}\,$V/m, and therefore several orders of
  magnitude below the noise levels of current EM instrument systems.
  Contour lines show the power of the amplitude of the signal.}
%

Another error test is shown in Figure~\ref{fig:skindepth1}. It shows in (a) the
amplitude of the analytical fullspace solution for a wide range of
resistivities and frequencies: $\rho=$ $10^{-10}\,\Omega\,$m to
$10^{10}\,\Omega\,$m, and $f =10^{-10}$\,Hz to $10^{14}$\,Hz. In this case, the
horizontal offset is set to the skin depth, and the vertical source-receiver
separation to a tenth of it, where the skin depth is given by \citep[e.g., ][
equation~1.49]{B.SEG.88.Ward}
%
\begin{equation}
  z_\mr{skin} = \left\{\frac{\omega^2 \varepsilon\mu}{2}
    \left[ \sqrt{1 + \frac{1}{\left(\omega\varepsilon\rho\right)^2}} -1\right]
  \right\}^{-1/2} \, , \\
  \label{eq:skin}
\end{equation}
%
where we used in the example $10\,\varepsilon_0$ for the electric permittivity
and $\mu_0$ for the magnetic permeability; $\omega = 2\pi f$. The grey contour
lines in the figure show the magnitude of the offset: the line with 0 is where
the offset is 1\,m, the line with 3 where the offset is 1\,km, etc. The contour
lines of the offset have a knee, after which they become almost independent of
frequency. This is where the quasi static approximation breaks down, and wave
phenomena become dominant. The red line indicates where $\omega\varepsilon\rho
= 1$. Subplot (b) shows the relative error of the DLF using the filter
\emph{Wer201} compared to the analytical solution. It shows nicely that the
filter can be used for all cases that are in the quasi static region, but not
outside.
%
\plot*{skindepth1}{width=.8\textwidth}{(a) Amplitude of the analytical
  fullspace solution for a wide range of resistivities and frequencies. The
  contour lines show the power of the offset used for the calculation, where
  the offset is set to the skin depth. (b) Relative error of the DLF compared
  with the analytical solution. The filter \emph{Wer201} works well in the
  diffusive limit, but fails when wave phenomena become dominant. The red
 line shows where $\omega\varepsilon\rho = 1$.}
%

@@

Figure~\ref{fig:GPR} shows the GPR example as calculated in
\cite{GEO.15.Hunziker} and \cite{GEO.17.Werthmuller}; the model parameters are
given in subplot (a). The filter used for this example for the Hankel transform
is a 2001\,pt filter, derived with the fullspace solution with $f=500\,$MHz for
the inversion and the check of quality. The whole space solution used
resistivity $200\,\Omega\,$m, relative permittivity $\varepsilon_\mr{r}=10$,
and permeability $\mu_\mr{r}=1$. Using Equation~\ref{eq:skin} yields a skin
depth of roughly 3.6\,m for these parameters. The source and receiver vertical
separation is 1\,m. For the Fourier transform a 4096\,pt FFT was used with
regularly spaced frequencies from 0.5\,MHz to 850\,MHz and then zero-padded up
to 2048\,MHz. The frequency result is multiplied with a Ricker wavelet with a
center frequency of 250\,MHz, and a gain function ($1 + |t^3|, t$ in ns) is
applied. Subplot (b) shows the result when using the adaptive quadrature (QUAD)
option of \texttt{empymod}, which uses the QAGSE routine from the Fortran
QUADPACK library. Subplot (c) shows the result using DLF with the new 2001\,pt
digital filter. The calculation with DLF took under 9 minutes and is therefore
roughly 80 times faster than the calculation with QUAD, which took roughly 11
hours and 27 minutes. Calculating the same model with QWE took 7 hours and 20
minutes. However, QWE uses in roughly 1/3 of the calculation internally QUAD in
this example, see \cite{GEO.17.Werthmuller}. Note that DLF was run in parallel
using 4 threads at once, taking effectively only 2 minutes and 10 seconds to
calculate.
% EMmod \citep{GEO.15.Hunziker} took for the same model about 18 hours 55
% minutes, using a 61\,pt Gauss-Kronrod integration routine.
The lagged convolution version of DLF and the splined version of QWE were used
in this comparison.
%
\plot*{GPR}{width=\textwidth}{GPR example for the model given in (a) using
  \texttt{empymod} with (b) \old{the} adaptive quadrature (QUAD) or with (c) a
  2001\,pt digital linear filter\old{ (b)}. QUAD took about 11\,h 27\,min to
  calculate, whereas DLF took 2\,min 10\,s in parallel on 4 nodes, hence under
  9\,min in total.}
%

Figure~\ref{fig:ftGPR} shows in (a)-(c) the real \new{and imaginary}
part\new{s} of the frequency domain results and in (d)-(f) the time domain
results for offsets of 0.2\,m, 2.0\,m, and 3.0\,m.
%
\plot*{ftGPR}{width=\textwidth}{The real\old{-part} \new{and imaginary parts of
the} frequency-domain \new{(a-c)} and the time-domain \new{(d-f)} responses for
offsets of (a/d) 0.2\,m, (b/e) 2.0\,m, and (c/f) 3.0\,m.}
%

The 2001\,pt filter was derived with the fullspace solution of a medium which
is very similar to the layer in which source and receiver reside in our GPR
example. To show that this filter can also be applied to different layer
parameters we run a test where we swapped layers one and two of the model in
Figure~\ref{fig:GPR} (a). The resulting real and imaginary parts for the
offsets 0.2\,m, 2.0\,m, and 3.0\,m are given in Figure~\ref{fig:ftGPR2nd}.
%
\plot*{ftGPR2nd}{width=\textwidth}{The real and imaginary parts of the
  frequency-domain response for the model given in Figure~\ref{fig:GPR} (a)
  with swapped first and second layers for offsets of (a) 0.2\,m, (b) 2.0\,m,
  and (c) 3.0\,m.}
%

>>>>

\subsection{Design}
Figures~\ref{fig:Figure-2-bw} and~\ref{fig:Figure-3-bw} show the solution spaces
of seven consecutive inversion runs using the following theoretical transform
pairs \citep[e.g.,][]{USGS.75.Anderson},
%
\begin{align}
  \int^\infty_0\,l \exp\left(-al^2\right) J_0(rl)\,dl &=
  \frac{1}{2a} \exp\left(\frac{-r^2}{4a}\right)\ , \\
  \int^\infty_0\,l^2 \exp\left(-al^2\right) J_1(rl)\,dl &=
  \frac{r}{4a^2} \exp\left(-\frac{r^2}{4a}\right)\ ,
  \label{eq:j01}
\end{align}
%
where $a$ was set to 5. In the algorithm you can provide one pair
for the inversion, and a different pair to get the minimum amplitude or the
maximum $r$. In this case the same transform pair was used for both the
inversion and the check of quality. The acceptable relative error was set to
1\,\%. The RHS evaluation parameter for the inversion was set so  that an
over-determined system was evaluated with $M = 2N$ equations, where $r_\mr{I}$
was logarithmically spaced from $\log_{10}[1/\max(b)] - 1$ to
$\log_{10}[1/\min(b)] + 1$, where $b$ are the filter abscissae as given in
equation~\ref{eq:base}. This is accomplished in \texttt{fdesign} by setting
parameter $r_\mr{def} = (1, 1, 2)$.

Figure~\ref{fig:Figure-2-bw} shows three different inversion runs for $N=101$,
201, and 401 for a wide range of spacing and shift values. From this one has to
decide for a filter length. Longer filters tend to give
more precise results, but their transform is computationally more expensive as
more values have to be evaluated. The length of the filter does not has to be
an odd number, but many published filters do have an odd number of
coefficients. The integral runs from $-\infty$ to $+\infty$ and hence an odd
point filter comes naturally by truncating the integral to a finite sum from
$-(N-1)/2$ to $(N-1)/2$. However, this is only true if the shift value
$\delta = 0$. If it differs from zero then there is no advantage in having an
odd point filter.
%
\plot*{Figure-2-bw}{width=\textwidth}{%
  Test of different filter lengths. Filter length is a trade-off between
    precision and speed, as shorter filters are faster but less precise, and
  longer filters are more precise but computationally more expensive. The red
  square in subplot (b) is the starting point of
  Figure~\ref{fig:Figure-3-bw}.}%
%

Figure~\ref{fig:Figure-3-bw} shows four consecutive inversion runs for $N=201$,
where each run is a focus on a subsection of the previous run, indicated by the
\old{red} square. From the low resolution overview runs (a) and (b) it looks
like this is a standard, straight-forward minimization problem. However, from
the more detailed results in (c) and (d) it becomes obvious that it is a
minimization problem that has to be solved stochastically, as there are
solutions with 2 orders of magnitude difference apparently randomly next to
each other.
%
\plot*{Figure-3-bw}{width=\textwidth}{%
  Solution spaces of four consecutive inversion runs for a 201\,pt filter. Each
  consecutive run zooms into a portion of the previous solution space,
  indicated by the \old{red} square. The more in detail we obtain the solution
  space, the more random appears to be the distribution.}%
%

Figure~\ref{fig:Figure-4-bw} shows in (a) the filter values for $J_0$ and $J_1$
of the best 201 \old{point}\new{pt} filter obtained this way, and in (b) its
right-hand-side solution. The black dots indicate negative values, from which
it can \new{be} seen that adjacent values are often alternating between
positive and negative contributions.
%
\plot*{Figure-4-bw}{width=.9\textwidth}{(a) Filter values of the best obtained
  201\,pt filter with the corresponding check of quality in (b). Black points
  indicate negative values, which shows that adjacent values have often
  opposite signs.}
%

Designing filters is to a large extent trial and error. All input variables
influence the outcome, and often an even better filter is found by sheer luck
of choosing the right starting parameters, as can be seen in
Figure~\ref{fig:Figure-4-bw} (h). However, once you are in this zone every
filter is a very good filter. Each of the input parameters has an effect on the
outcome. It also depends heavily on the transform pairs $f_\mr{I;C}$; functions
that decay rapidly are generally better, as noted by earlier authors
\citep[e.g.][]{USGS.75.Anderson}. It also depends on the filter length, and
obviously heavily on the spacing and shift values. Another important point is
how you define the right-hand evaluation points of the inversion
($r_\mr{def}$). Evaluating corresponding transform pairs separately or jointly
also leads to different filter coefficients ($J_0$, $J_1$, or $J_0$ \& $J_1$,
or equally sine, cosine, or sine \& cosine); also if the real or the imaginary
part is used when complex transform pairs or \texttt{empymod} is used; and if
it is inverted for the minimum amplitude or for the maximum $r$.

@@

It is very important to note again that other scenarios might yield very
different error plots. Although the new 201\,pt filter proves to be very
accurate for these three models, it might not be the best filter in other
cases. To verify the applicability of the filter we run two different tests
over a wide range of scenarios. Figure~\ref{fig:Figure-7} shows the relative
errors of DLF using the filter \emph{Wer201} compared to QWE for a deep water
model \new{(2\,km water depth)}, a shallow water model \new{(400\,m water
depth)}, and a land model. The models consist of air (upper halfspace), a water
layer in the first two examples, and a subsurface halfspace. Source depth is
1990\,m, 10\,m, and 0.5\,m in the deep, shallow, and land case, respectively.
Receiver depth is 2000\,m, 100\,m, and 0.8\,m. The subsurface halfspace
resistivity varies from 1 to 10, 100, and 1000\,$\Omega\,$m from the left to
the right column. The error plots cover offsets from 50\,m to 20\,km on the
x-axis, and 0.01\,Hz to 10\,Hz on the y-axis. It can be seen in the result that
the filter is sufficiently precise for all practical CSEM cases, hence has
generally an error far below 1\,\% ($10^{-2}$) in all cases. A relative noise
of less than 1\,\% is generally considered really good for real data. The
exceptions are in the shallow water case at large offsets with relatively high
frequencies, e.g., 10\,km offset with 8\,Hz; this zone has a very high error
for subsurface resistivities of 1\,$\Omega\,$m and 10\,$\Omega\,$m (yellow
zones). However, this is due to the fact that the amplitudes of the signal for
these offsets and frequencies are in the order of $10^{-25}\,$V/m. The grey
contour lines in the plot indicate the power of the amplitude of the signal.
%
\plot*{Figure-7}{width=\textwidth}{Relative error plots comparing the DLF
  (\emph{Wer201}) with QWE for the three cases deep water (top row), shallow
  water (middle row), and land (bottom row). The subsurface halfspace
  resistivity varies from 1 to 1000\,$\Omega\,$m from the left column to the
  right column; offsets vary from 50\,m to 20\,km, and frequencies vary from
  0.01\,Hz to 10\,Hz. The DLF provides sufficiently accurate results for all
  practical CSEM applications. The exception is in the shallow water case for
  $\rho = 1\,\Omega\,$m and $10\,\Omega\,$m for large offsets and high
  frequencies (yellow zones). However, the amplitudes in these regions are in
  the order of $10^{-25}\,$V/m, and therefore several orders of
  magnitude below the noise levels of current EM instrument systems.
  Contour lines show the power of the amplitude of the signal.}
%

Another error test is shown in Figure~\ref{fig:Figure-8}. It shows in (a) the
amplitude of the analytical fullspace solution for a wide range of
resistivities and frequencies: $\rho=$ $10^{-10}\,\Omega\,$m to
$10^{10}\,\Omega\,$m, and $f =10^{-10}$\,Hz to $10^{14}$\,Hz. In this case, the
horizontal offset is set to the skin depth, and the vertical source-receiver
separation to a tenth of it, where the skin depth is given by \citep[e.g., ][
equation~1.49]{B.SEG.88.Ward}
%
\begin{equation}
  z_\mr{skin} = \left\{\frac{\omega^2 \varepsilon\mu}{2}
    \left[ \sqrt{1 + \frac{1}{\left(\omega\varepsilon\rho\right)^2}} -1\right]
  \right\}^{-1/2} \, , \\
  \label{eq:skin}
\end{equation}
%
where we used in the example $10\,\varepsilon_0$ for the electric permittivity
and $\mu_0$ for the magnetic permeability; $\omega = 2\pi f$. The grey contour
lines in the figure show the magnitude of the offset: the line with 0 is where
the offset is 1\,m, the line with 3 where the offset is 1\,km, etc. The contour
lines of the offset have a knee, after which they become almost independent of
frequency. This is where the quasi static approximation breaks down, and wave
phenomena become dominant. The red line indicates where $\omega\varepsilon\rho
= 1$. Subplot (b) shows the relative error of the DLF using the filter
\emph{Wer201} compared to the analytical solution. It shows nicely that the
filter can be used for all cases that are in the quasi static region, but not
outside.
%
\plot*{Figure-8}{width=.8\textwidth}{(a) Amplitude of the analytical
  fullspace solution for a wide range of resistivities and frequencies. The
  contour lines show the power of the offset used for the calculation, where
  the offset is set to the skin depth. (b) Relative error of the DLF compared
  with the analytical solution. The filter \emph{Wer201} works well in the
  diffusive limit, but fails when wave phenomena become dominant. The red
 line shows where $\omega\varepsilon\rho = 1$.}
%

@@

Figure~\ref{fig:Figure-9} shows the GPR example as calculated in
\cite{GEO.15.Hunziker} and \cite{GEO.17.Werthmuller}; the model parameters are
given in subplot (a). The filter used for this example for the Hankel transform
is a 2001\,pt filter, derived with the fullspace solution with $f=500\,$MHz for
the inversion and the check of quality. The whole space solution used
resistivity $200\,\Omega\,$m, relative permittivity $\varepsilon_\mr{r}=10$,
and permeability $\mu_\mr{r}=1$. Using Equation~\ref{eq:skin} yields a skin
depth of roughly 3.6\,m for these parameters. The source and receiver vertical
separation is 1\,m. For the Fourier transform a 4096\,pt FFT was used with
regularly spaced frequencies from 0.5\,MHz to 850\,MHz and then zero-padded up
to 2048\,MHz. The frequency result is multiplied with a Ricker wavelet with a
center frequency of 250\,MHz, and a gain function ($1 + |t^3|, t$ in ns) is
applied. Subplot (b) shows the result when using the adaptive quadrature (QUAD)
option of \texttt{empymod}, which uses the QAGSE routine from the Fortran
QUADPACK library. Subplot (c) shows the result using DLF with the new 2001\,pt
digital filter. The calculation with DLF took under 9 minutes and is therefore
roughly 80 times faster than the calculation with QUAD, which took roughly 11
hours and 27 minutes. Calculating the same model with QWE took 7 hours and 20
minutes. However, QWE uses in roughly 1/3 of the calculation internally QUAD in
this example, see \cite{GEO.17.Werthmuller}. Note that DLF was run in parallel
using 4 threads at once, taking effectively only 2 minutes and 10 seconds to
calculate.
% EMmod \citep{GEO.15.Hunziker} took for the same model about 18 hours 55
% minutes, using a 61\,pt Gauss-Kronrod integration routine.
The lagged convolution version of DLF and the splined version of QWE were used
in this comparison.
%
\plot*{Figure-9}{width=\textwidth}{GPR example for the model given in (a) using
  \texttt{empymod} with (b) \old{the} adaptive quadrature (QUAD) or with (c) a
  2001\,pt digital linear filter\old{ (b)}. QUAD took about 11\,h 27\,min to
  calculate, whereas DLF took 2\,min 10\,s in parallel on 4 nodes, hence under
  9\,min in total.}
%

Figure~\ref{fig:Figure-10-bw} shows in (a)-(c) the real \new{and imaginary}
part\new{s} of the frequency domain results and in (d)-(f) the time domain
results for offsets of 0.2\,m, 2.0\,m, and 3.0\,m.
%
\plot*{Figure-10-bw}{width=\textwidth}{The real\old{-part} \new{and imaginary
  parts of the} frequency-domain \new{(a-c)} and the time-domain \new{(d-f)}
  responses for \new{horizontal} offsets of (a/d) 0.2\,m, (b/e) 2.0\,m, and
  (c/f) 3.0\,m.}
%

The 2001\,pt filter was derived with the fullspace solution of a medium which
is very similar to the layer in which source and receiver reside in our GPR
example. To show that this filter can also be applied to different layer
parameters we run a test where we swapped layers one and two of the model in
Figure~\ref{fig:Figure-9} (a). The resulting real and imaginary parts for the
offsets 0.2\,m, 2.0\,m, and 3.0\,m are given in Figure~\ref{fig:Figure-11-bw}.
%
\plot*{Figure-11-bw}{width=\textwidth}{The real and imaginary parts of the
  frequency-domain response for the model given in Figure~\ref{fig:Figure-9}
  (a) with swapped first and second layers for \new{horizontal} offsets of (a)
  0.2\,m, (b) 2.0\,m, and (c) 3.0\,m.}
%
